### 2014-10-15 fundamentals/intro.tex
background edits

Methods for calculating those metrics vary among simulators. Some model the 
system of facilities, economics, and materials at static equillibrium, while 
others capture its dynamics.  
Similarly, while some simulators discretely model material and facilities, 
others treat materials in streams and facilities in fleets, in an aggregated 
fashion. Depending on their intended use, simulators often overspecialize, 
modeling a single aspect of the fuel cycle in great detail while neglecting 
others. A simulator created for policy modeling might have excellent 
capability in economics while material isotopics and transmutation detail are 
neglected.

Historically, the national laboratories have driven development and regulated 
the use of their own tools such as \gls{VISION}\cite{jacobson_verifiable_2010}, 
\gls{DANESS}\cite{van_den_durpel_daness_2009}, 
\gls{DYMOND}\cite{modeling_yacout_2005}, and 
\gls{NFCSim}\cite{schneider_nfcsim:_2005}. With limited access to those tools, 
universities and industry have simultaneously developed tools of their own, 
such as \gls{CAFCA}\cite{guerin_benchmark_2006} and \gls{COSI}\cite{cosi}.

The \Cyclus simulator arose out of the 
\gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code. That software 
itself was the result of lessons-learned from an \gls{LDRD} project at 
\gls{INL}, 
\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006} which 
captured regional behaviors in fuel cycle scenarios.

>>>>

Historically, researchers create new nuclear fuel cycle simulation tools when 
existing tools are not available or not sufficiently general to calculate their 
metrics of interest with their method of choice.

Historically, the national laboratories have driven development and regulated 
the use of their own tools such as \gls{VISION}\cite{jacobson_verifiable_2010}, 
\gls{DANESS}\cite{van_den_durpel_daness_2009}, 
\gls{DYMOND}\cite{modeling_yacout_2005}, and 
\gls{NFCSim}\cite{schneider_nfcsim:_2005}. With limited access to those tools 
and a need to customize them for research purposes, 
universities and private industry researchers ``reinvent the wheel'' by 
developing tools of their own from scratch and tailored to their own needs (e.g., 
\gls{CAFCA}\cite{guerin_benchmark_2006} and \gls{COSI}\cite{cosi} 
respectively).

This cycle has resulted in a a proliferation of specialized, limited-access 
fuel cycle simulators for the calculation of fuel cycle metrics, and methods 
for calculating those metrics vary among simulators. Some model the 
system of facilities, economics, and materials at static equillibrium, while 
others capture its dynamics.  
Similarly, while some simulators discretely model material and facilities, 
others treat materials in streams and facilities in fleets, in an aggregated 
fashion. Depending on their intended use, simulators often overspecialize, 
modeling a single aspect of the fuel cycle in great detail while neglecting 
others. A simulator created for policy modeling might have excellent 
capability in economics while material isotopics and transmutation detail are 
neglected.

When the \Cyclus simulator arose out of the 
\gls{GENIUSv2}\cite{oliver_studying_2009,huff_geniusv2_2009} code
was the result of lessons-learned from an \gls{LDRD} project at 
\gls{INL}, 
\gls{GENIUSv1}\cite{dunzik-gougar_global_2007,jain_transitioning_2006} which 
captured regional behaviors in fuel cycle scenarios.
